%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \usepackage{fontawesome5} % removed — icons replaced with plain text for ATS compatibility
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.6in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}
\begin{center}
    {\Huge \scshape Tanay Agarwal} \\ \vspace{4pt}
    \small 
    Mumbai, India $|$
    +91 9136863765 $|$
    \href{mailto:agarwal.tanay28@gmail.com}{\underline{agarwal.tanay28@gmail.com}} $|$
    \href{https://www.linkedin.com/in/tanay-agarwal-43b39520b/}{\underline{LinkedIn}} $|$
    \href{https://github.com/tanaytemani}{\underline{GitHub}} $|$
    \href{https://www.tanayagarwal.online}{\underline{Portfolio}}
    \vspace{-5pt}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{AI/ML Engineer with 2+ years of experience designing and deploying production multi-agent AI systems and enterprise chatbots. Built autonomous agent ecosystems of 15+ agents integrated with HubSpot, Salesforce, and Jira, and delivered 3 generative AI chatbots serving cross-functional teams. Proven track record in agentic AI, RAG pipelines, and computer vision across insurance, manufacturing, and financial services.}
\vspace{-5pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {TheAgentic (Zenith Software Limited)}{May 2025 - Present}
      {\textbf{Artificial Intelligence Developer}}{}
      \resumeItemListStart
            \resumeItem{Built and productionized multi-agent AI systems using PydanticAI, enabling autonomous document intelligence, structured data extraction, and agent-orchestrated reasoning across enterprise knowledge bases.}
            \resumeItem{Developed enterprise-scale autonomous agent ecosystems (15+ agents) for CRM, onboarding, and lifecycle analytics---integrated with HubSpot, Salesforce, Slack, Gmail, and Jira---delivering end-to-end AI automation.}
            \resumeItem{Designed retrieval-augmented reasoning, policy-intelligence, and strategic-recommendation agents to generate insights and support expert decision-making in insurance and financial domains.}
            \resumeItem{Implemented multimodal AI pipelines, including vision-augmented and web-intelligence agents for deep research, data collection, and risk analysis.}
        \resumeItemListEnd

  \resumeSubheading
      {Saint Gobain - INDEC}{Jun 2024 - May 2025}
      {\textbf{Associate Software Engineer}}{}
      \resumeItemListStart
            \resumeItem{Built data pipelines using Snowflake, Azure Data Factory, and Azure Synapse Analytics; earned two Snowflake Badges (Data Warehouse, Data Engineering).}
            \resumeItem{Developed an HR Chatbot using LangChain to automate employee queries on policies, payroll, and benefits, reducing manual HR ticket volume.}
            \resumeItem{Engineered a BookOfIT Chatbot with Knowledge Graphs and LangGraph Agents to consolidate Confluence data into an interactive, multi-step knowledge hub.}
            \resumeItem{Built a ServiceNow Chatbot leveraging LangGraph Agents for automated IT ticket creation and sequential multi-step resolution workflows.}
        \resumeItemListEnd

    \resumeSubheading
      {Shunya Dot Ek}{Feb 2023 - Aug 2023}
      {\textbf{Machine Learning Intern}}{}
      \resumeItemListStart
            \resumeItem{Improved Divya Drishti product accuracy to 97.6\% by training and optimizing deep learning models for computer vision.}
            \resumeItem{Implemented object detection and tracking pipelines using YOLO, Faster-RCNN, and OpenCV for product recognition and movement analysis.}
        \resumeItemListEnd

    \resumeSubheading
      {ICICI Prudential Life Insurance}{Aug 2022 - Dec 2022}
      {\textbf{Software Engineer Intern}}{}
      \resumeItemListStart
            \resumeItem{Reduced Bloomberg job file transfer time by over 40\% by automating project payment file transfers.}
            \resumeItem{Collaborated with the IT-SAP team to gather business requirements and configure SAP system workflows.}
            \resumeItem{Automated Host-to-Host file transfers for the Investment Rationale Project, streamlining payment operations.}
        \resumeItemListEnd

    
  \resumeSubHeadingListEnd
\vspace{-8pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DJ Sanghvi College of Engineering, Mumbai}{2024}
      {B.Tech, CSE (Data Science)}{CGPA : 8.9}
  \resumeSubHeadingListEnd
\vspace{-8pt}

%------------TECHNICAL SKILLS------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
    \textbf{AI \& LLM Ecosystem:}{
    Agentic AI, PydanticAI, LangChain, LangGraph, CrewAI, RAG Pipelines, Vector Databases, Knowledge Graphs, 
    LLM Orchestration, Prompt Engineering, NLP, Multimodal AI} \\[3pt]
    \textbf{Machine Learning:}{
    TensorFlow, PyTorch, Deep Learning, Computer Vision, YOLO, CNNs, Transformers} \\[3pt]
    \textbf{Data / Backend:}{
    SQL, PostgreSQL, Snowflake, Azure Data Factory (ADF), Azure Synapse Analytics, FastAPI, Apache Spark, Kafka, Hadoop} \\[3pt]
    \textbf{Programming:}{
    Python, Java, C, JavaScript} \\[3pt]
    \textbf{DevOps / Tools:}{
    Docker, Kubernetes, Linux, GitHub, Bash, React, Node.js} \\[3pt]
    \textbf{Certifications:}{
    AWS Cloud Architect, AWS Data Analytics, AWS Data Engineering, Snowflake Data Warehouse, Snowflake Data Engineering} \\
}}
\end{itemize}


\end{document}
